\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-01-31 eg6-letters/NIM/EG6_RTPC_NIM.tex
added updated plots and cleaning the coherent asymmetry phi plot

\begin{abstract}
A new Radial Time Projection Chamber (RTPC) was developed at Jefferson 
laboratory (JLab) to track low-energy nuclear recoils for the purpose of 
measuring nuclear exclusive channels, such as, coherent Deeply Virtual Compton 
Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
processes, $^4$He nucleus remains intact and recoils as a whole in the final 
state. The CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for 
similar studies on proton targets, however it cannot track recoils with momenta 
less than 250 MeV/c. In 2009, we carried out measurements on $^4$He target 
using CLAS spectrometer, which was upgraded with the RTPC during the CLAS-EG6 
experimental run. The detector was positioned directly around a gaseous target, 
allowing a detection threshold of $~$100  MeV/c for $^4$He. This article 
discuses the RTPC design, work principle, calibration methods and 
performances.
\end{abstract}

>>>>

\begin{abstract}
A new Radial Time Projection Chamber (RTPC) was developed at Jefferson 
laboratory (JLab) to track low-energy nuclear recoils for the purpose of 
measuring nuclear exclusive channels, such as, coherent Deeply Virtual Compton 
Scattering (DVCS) and coherent production of mesons on $^4$He. In such 
processes, $^4$He nucleus remains intact and recoils as a whole in the final 
state. The CEBAF Large Acceptance Spectrometer (CLAS) at JLab has been used for 
similar studies on proton targets, however it cannot track recoils with momenta 
less than 250 MeV/c. In 2009, we carried out measurements on $^4$He target 
using CLAS spectrometer, which was supplemented with the RTPC during the 
CLAS-EG6 experimental run. The detector was positioned directly around a 
gaseous target, allowing a detection threshold as low as $~$100  MeV/c for 
$^4$He. This article discuses the RTPC design, work principle, calibration 
methods and performances.
\end{abstract}
